### 2020-08-24 benchmarking/benchmarkingVM/ESS_round3.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-10 15:55:24
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [adapt (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [Bactrian (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 76.35) --
	(212.73,289.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.35,289.08) --
	(271.35,195.00) --
	( 76.35,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 50.90) --
	(238.18,289.08);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.35,289.08) --
	(271.35,220.45) --
	( 50.90,  0.00);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 25.45) --
	(263.63,289.08);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (271.35,289.08) --
	(271.35,245.90) --
	( 25.45,  0.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (145.42, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,150.12) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.97, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,124.67) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.53, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 99.22) {$4\times$};

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.97,173.04) --
	(174.56,173.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.02,163.26) --
	(170.02,179.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.02,169.15) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,172.12) --
	(172.25,172.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.32,170.07) --
	(170.32,173.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.32,167.26) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.73,184.48) --
	(183.91,184.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.85,183.02) --
	(182.85,185.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.85,179.62) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.83,152.06) --
	(151.70,152.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.43,146.58) --
	(145.43,156.28);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.43,147.20) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.34,176.95) --
	(176.22,176.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.31,171.72) --
	(172.31,181.01);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.31,173.45) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.52,189.61) --
	(189.61,189.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.07,189.39) --
	(189.07,189.83);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.07,186.11) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,177.49) --
	(176.50,177.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.34,177.31) --
	(174.34,177.66);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.34,173.60) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.00,179.60) --
	(179.72,179.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.96,177.03) --
	(177.96,181.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.96,174.74) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.92,182.73) --
	(183.11,182.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.02,182.56) --
	(183.02,182.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.02,177.87) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.08,144.73) --
	(143.52,144.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.58,137.44) --
	(140.58,149.93);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.58,139.87) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.53,157.68) --
	(164.32,157.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.84,139.80) --
	(160.84,166.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.84,154.18) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.53,191.09) --
	(191.56,191.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.05,190.40) --
	(191.05,191.75);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.05,187.59) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.25,170.79) --
	(183.76,170.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.21,169.12) --
	(181.21,172.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.21,166.90) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.52,175.16) --
	(188.36,175.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.10,159.21) --
	(182.10,183.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.10,170.30) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.87,190.74) --
	(190.95,190.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.41,189.74) --
	(190.41,191.69);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.41,185.88) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.08,153.71) --
	(157.42,153.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.97,149.99) --
	(152.97,156.80);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.97,148.85) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.95,170.40) --
	(184.11,170.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.10,167.27) --
	(180.10,173.07);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.10,166.90) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.12,201.71) --
	(203.34,201.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.27,200.95) --
	(202.27,202.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (202.27,198.21) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.27, 60.00) -- (102.27, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 60.00) -- (144.54, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.81, 60.00) -- (186.81, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.27, 38.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (144.54, 38.40) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (186.81, 38.40) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.08, 38.40) {10000};

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-24 19:05:08
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/chain [adapt (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/chain [Bactrian (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 71.00) --
	(218.08,289.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,197.39) --
	( 71.00,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 47.34) --
	(241.74,289.08);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,221.06) --
	( 47.34,  0.00);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 23.67) --
	(265.41,289.08);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,244.72) --
	( 23.67,  0.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};

@@

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.31,201.61) --
	(201.01,201.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.48,192.53) --
	(196.48,207.50);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.48,197.72) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.79,219.42) --
	(219.22,219.42);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.59,218.48) --
	(217.59,220.32);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (217.59,214.56) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.04,212.68) --
	(212.00,212.68);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.05,211.52) --
	(211.05,213.76);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (211.05,207.82) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.45,182.57) --
	(182.46,182.57);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.56,176.26) --
	(176.56,187.17);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.56,177.71) {$h$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.12,205.91) --
	(202.50,205.91);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.21,201.26) --
	(199.21,209.56);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.21,202.41) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.46,217.34) --
	(217.37,217.34);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.92,217.08) --
	(216.92,217.59);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (216.92,213.84) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.40,193.34) --
	(208.66,193.34);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.04,186.76) --
	(208.04,198.08);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (208.04,189.45) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.80,188.26) --
	(189.91,188.26);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.89,186.60) --
	(188.89,189.77);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.89,183.40) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.67,218.00) --
	(215.97,218.00);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.82,217.74) --
	(215.82,218.26);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (215.82,213.14) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.78,199.74) --
	(200.22,199.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.04,198.72) --
	(199.04,200.70);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.04,194.88) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.96,201.61) --
	(210.35,201.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.67,200.11) --
	(209.67,202.99);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (209.67,198.11) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.54,216.76) --
	(216.99,216.76);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.77,216.10) --
	(216.77,217.39);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (216.77,213.26) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.20,193.91) --
	(203.44,193.91);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.61,191.58) --
	(200.61,195.96);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.61,190.02) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.98,209.31) --
	(212.21,209.31);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.38,208.84) --
	(209.38,209.77);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (209.38,204.45) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.94,210.71) --
	(211.30,210.71);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.12,210.10) --
	(211.12,211.29);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (211.12,205.85) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.13,177.83) --
	(174.32,177.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.10,173.05) --
	(171.10,181.55);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.10,172.97) {$h$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.94,189.00) --
	(195.48,189.00);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.01,181.20) --
	(191.01,194.33);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.01,185.50) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.33,218.47) --
	(219.07,218.47);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.70,217.85) --
	(218.70,219.07);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.70,214.97) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.44,174.86) --
	(203.81,174.86);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.09,167.36) --
	(198.09,180.05);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.09,170.97) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.81,195.50) --
	(201.63,195.50);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.74,190.50) --
	(200.74,199.36);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.74,190.64) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.63,221.84) --
	(225.94,221.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.79,220.41) --
	(225.79,223.15);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (225.79,216.98) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.36,192.17) --
	(195.11,192.17);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.79,190.64) --
	(193.79,193.58);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.79,187.31) {$h$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.47,178.14) --
	(203.54,178.14);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.63,172.95) --
	(201.63,182.11);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (201.63,174.64) {$\sigma$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.71,218.09) --
	(219.01,218.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.37,217.44) --
	(218.37,218.71);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.37,214.59) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.19,185.19) --
	(207.71,185.19);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.97,176.99) --
	(206.97,190.71);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.97,181.30) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.01,189.58) --
	(213.79,189.58);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.46,182.79) --
	(212.46,194.43);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.46,184.72) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.79,213.27) --
	(212.25,213.27);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.02,212.31) --
	(212.02,214.18);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.02,208.41) {$r$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.97,195.85) --
	(186.82,195.85);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.92,193.43) --
	(185.92,197.98);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.92,190.99) {$h$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.76,187.74) --
	(189.34,187.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.20,186.56) --
	(187.20,188.84);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.20,184.24) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.20,218.21) --
	(219.95,218.21);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.10,214.91) --
	(219.10,220.97);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (219.10,214.71) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.49,195.91) --
	(210.85,195.91);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.56,188.71) --
	(207.56,200.95);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (207.56,192.02) {$p$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.88,186.94) --
	(190.98,186.94);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.20,179.46) --
	(188.20,192.12);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.20,182.08) {$L$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.06,217.95) --
	(217.87,217.95);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.47,217.06) --
	(217.47,218.80);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (217.47,213.09) {$r$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.47,184.35) --
	(186.44,184.35);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.54,181.55) --
	(182.54,186.76);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.54,179.49) {$h$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.51,198.78) --
	(209.36,198.78);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.89,194.94) --
	(205.89,201.91);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (205.89,195.28) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.63,228.33) --
	(230.02,228.33);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.87,227.50) --
	(228.87,229.12);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (228.87,224.83) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (217.25, 60.00);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.31, 60.00) -- ( 99.31, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.62, 60.00) -- (138.62, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93, 60.00) -- (177.93, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.25, 60.00) -- (217.25, 54.00);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.31, 38.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (138.62, 38.40) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (177.93, 38.40) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (217.25, 38.40) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,217.25);
